\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-18 draft.tex
rough in example for proof of prop:bothbribe

\subsection{Two Vote Buyers}		
Now we consider the entire game by adding Vote Buyer $A$'s choice of bribes. Vote Buyer A's first order conditions are more complicated than those of Vote Buyer $B$ because her choices $\bm a$ will impact those of Vote Buyer $B$.

@@

\begin{proposition}
  It is possible for both vote buyers to bribe legislators on the same vote.
	\label{res:bothbribe}
\end{proposition}

@@

>>>>

\subsection{Two Vote Buyers}
\label{sec:two}
Now we consider the entire game by adding Vote Buyer $A$'s choice of bribes. Vote Buyer A's first order conditions are more complicated than those of Vote Buyer $B$ because her choices $\bm a$ will impact those of Vote Buyer $B$.

@@

\begin{proposition}
  It is possible for both vote buyers to bribe legislators on the same vote.
	\label{prop:bothbribe}
\end{proposition}

@@

\vskip.3in
\noindent \textbf{\hypertarget{Pr_bothbribe}{Proof of Proposition~\ref{prop:bothbribe}}}: \\
Take the following example. Let $\al=0$ so that the means of the ideal point distribution for the three legislators are $-\frac{1}{2}$, $0$ and $\frac{1}{2}$. Let the willingness-to-pay parameters be $W_A = 6$ and $W_B = 8$. And let the scale parameters for the legislators at $0$ and $\frac{1}{2}$ be 1 and $s_{-\frac{1}{2}} = 1.1$.

In this example, the optimal bribe offer function for Vote Buyer $A$ is to offer nothing to the legislators at $0$ and $\frac{1}{2}$ and $a_{-\frac{1}{2}}=0.4$. Vote Buyer $B$ responds by offering nothing to the legislators at $-\frac{1}{2}$ and $\frac{1}{2}$ and $b_0 = 0.21$ to the legislator at zero. The final gross positions of the mean parameters for the three legislators are, from left to right, $\left\{ -0.1, -0.21, 0.5 \right\}$, with one legislator each being lobbied in each direction.
